Compiling refinement types to dependent types

### 2020-07-09 tex/paper.tex
Add shorthand \Int and \Unit commands

@@

The surface language might also have other base types (for example, $\mathbf{Int}$),
elements of syntax (like numbers and operations on them)
as well as typing rules relating those,
but we omit them for the sake of brevity.

We also have the following concessions:
\begin{itemize}
  \item The syntax only allows refinements on base types.
    Note that this does not restrict the expressive power of the language.
    For instance, a refinement on a function that we might otherwise wish to write as
    \[
      (x : \mathbf{Int}) \rightarrow \{ v : \mathbf{Int} \rightarrow \mathbf{Int} | v x = 0 \} \rightarrow \mathbf{Int}
    \]
    might instead be expressed via a dummy parameter:
    \[
      (x : \mathbf{Int}) \rightarrow (f : \mathbf{Int} \rightarrow \mathbf{Int}) \rightarrow \{ \_ : \mathbf{Unit} | f x = 0 \} \rightarrow \mathbf{Int}.
    \]
\end{itemize}

>>>>

\newcommand{\Unit}{\textbf{Unit}}
\newcommand{\Int}{\textbf{Int}}

@@

The surface language might also have other base types (for example, $\Int$),
elements of syntax (like numbers and operations on them)
as well as typing rules relating those,
but we omit them for the sake of brevity.

We also have the following concessions:
\begin{itemize}
  \item The syntax only allows refinements on base types.
    Note that this does not restrict the expressive power of the language.
    For instance, a refinement on a function that we might otherwise wish to write as
    \[
      (x : \Int) \rightarrow \{ v : \Int \rightarrow \Int | v x = 0 \} \rightarrow \Int
    \]
    might instead be expressed via a dummy parameter:
    \[
      (x : \Int) \rightarrow (f : \Int \rightarrow \Int) \rightarrow \{ \_ : \Unit | f x = 0 \} \rightarrow \Int.
    \]
\end{itemize}
